### 2018-08-28 manuscript.tex
Update manuscript.tex

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters in the hope of???

>>>>

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters (structural models) in the hope of???
